\LARGE \bf Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs

### 2020-12-10 icra-2021.tex
re-written certain sections to be complaint with the data-driven control approach

The remainder of the paper is organized as follows. The overview of dynamic planning is provided in Section~\ref{sec:prob}, along with a suitable model for the position and energy. The algorithm is proposed in Section~\ref{sec:algo}. Section~\ref{sec:experimental} presents the result and showcases the performances. We propose some conclusions in Section~\ref{sec:conclusion}. Finally, we provide some additional information and examples in Appendixes~\ref{app:proof-eqv}--\ref{app:simulator}.

@@

The algorithm takes as input a user-specified initial plan that consists of different stages and some initial guesses that are necessary for the position and energy estimation. At each stage, the UAV must follow the trajectory within the trajectory constraints set and do the computations within the computations constraints sets. There is one trajectory constraints set but multiple computations constraints sets, one per each computation parameter. The algorithm outputs the new position, the instantaneous energy consumption, and the control (the parameters).

@@

\subsection{State: position $\mathbf{p}$}
\label{sec:model}

We model the position with $(x,y)\in\mathbf{p}$ coordinates and the altitude $h$, and derive its evolution using vector field~\cite{de2017guidance}.

Let us assume that the set
\begin{equation}\label{eq:area}
  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i\},
\end{equation}
delimits the area where the $i$-th trajectory $\varphi_i$ is free to evolve using the trajectory parameters $c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:tee1}). $\varphi_i$ is a function of the two coordinates and is equal to zero when a point $\mathbf{p}_k$ is on the trajectory. Physically, this means the UAV is flying exactly over the nominal trajectory. The trajectory parameters allows to change the trajectory. They are a way to alter the nominal trajectory in the initial plan.
In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal trajectory parameters $c_i^0$ (here we again neglect for simplicity the $\sigma=0$ computations parameters), such that $\varphi_i(\mathbf{p}_k,c_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).

We derive the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=\begin{bmatrix}\partial\varPhi/\partial x & \partial\varPhi/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector
\begin{equation}\label{eq:pd}
  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
    0&1\\-1&0
  \end{bmatrix},
\end{equation}
where $E$ specifies the rotation (which influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence. The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the uncertainty, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:tee1}).

\subsection{State: energy $\mathbf{q}$}
\label{sec:energy-model}

We model the energy using some energy coefficients $\mathbf{q}\in\mathbb{R}^m$ that characterize the energy signal. We refer to the instantaneous energy consumption evolution simply as the energy signal. The coefficients are derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series).

@@

>>>>

The remainder of the paper is organized as follows. The overview of dynamic planning is provided in Section~\ref{sec:prob}, and a suitable model for the energy in Section~\ref{sec:energy-model}. The algorithm is proposed in Section~\ref{sec:algo}. Section~\ref{sec:experimental} presents the result and showcases the performances. We propose some conclusions in Section~\ref{sec:conclusion}. Finally, we provide some additional information and examples in Appendixes~\ref{app:proof-eqv}--\ref{app:simulator}.

@@

The algorithm plans the path and computations from a user-specified initial plan that consists of different stages and some initial guesses that are necessary for the position and energy estimation. At each stage, the UAV must follow a trajectory within the trajectory constraints set and do the computations within the computations constraints sets. There is one trajectory constraints set but multiple computations constraints sets, one per each computation parameter. The algorithm outputs the control (the parameters), the new position, and the energy consumption. The UAV utilizes the control to alter its energy consumption to meet the energy budget. The control is data-driven. Energy sensor data refine a perfect energy model used to predict future energy consumption and derive the optimal control.

@@

\section{Periodic Energy Model}
\label{sec:energy-model}

We model the energy using some energy coefficients $\mathbf{q}\in\mathbb{R}^m$ that characterize the energy signal. We refer to the instantaneous energy consumption evolution simply as the energy signal. The coefficients are derived from Fourier analysis (the size of the energy coefficients vector $m$ is related to the order of a Fourier series) and estimated using a state estimator (Kalman filter).

@@

\subsection{Trajectory parameters energy contribution}
\label{sec:model}

Let us assume that the set
\begin{equation}\label{eq:area}
  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i\},
\end{equation}
delimits the area where the $i$-th trajectory $\varphi_i$ is free to evolve using the trajectory parameters $c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:tee1}). $\varphi_i$ is a function of the two coordinates and is equal to zero when a point $\mathbf{p}_k$ is on the trajectory. Physically, this means the UAV is flying exactly over the nominal trajectory. The trajectory parameters allows to change the trajectory. They are a way to alter the nominal trajectory in the initial plan and thus alter the energy signal.
In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal trajectory parameters $c_i^0$ (here we again neglect for simplicity the $\sigma=0$ computations parameters), such that $\varphi_i(\mathbf{p}_k,c_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget).

We derive the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=\begin{bmatrix}\partial\varPhi/\partial x & \partial\varPhi/\partial y\end{bmatrix}^T$, and the direction to follow in the form of velocity vector~\cite{de2017guidance}
\begin{equation}\label{eq:pd}
  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
    0&1\\-1&0
  \end{bmatrix},
\end{equation}
where $E$ specifies the rotation (which influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence. The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the uncertainty, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:tee1}).
